% arara: pdflatex: { synctex: yes }
% arara: makeindex: { style: ctuthesis }
% arara: bibtex

% The class takes all the key=value arguments that \ctusetup does,
% and a couple more: draft and oneside
\documentclass[twoside]{ctuthesis}
\input{_my_pkg.tex}
\input{_glossary.tex}
\addbibresource{BAP_bibliography.bib}


\ctusetup{
	% preprint = \ctuverlog,
	% mainlanguage = english,
%	titlelanguage = czech,
	mainlanguage = english,
	otherlanguages = {czech},
	title-czech = {Návrh platformy pro 2D LiDAR},
	title-english = {Design of a platform for 2D LiDAR},
	doctype = B,
	faculty = F3,
	department-czech = {Katedra radioelektroniky},
	department-english = {Department of Radioelectonics},
	author = {Illia Novosad},
	supervisor = {Ing. Pavel Puričer, Ph.D.},
	fieldofstudy-english = {Electronics and Communications},
	fieldofstudy-czech = {Elektronika a komunikace},
	keywords-czech = {LiDAR, 3D rekonstrukce, point cloud, zpracování signálů, mapování},
	keywords-english = {LiDAR, 3D reconstruction, point cloud, signal processing, mapping},
	day = 13,
	month = 11,
	year = 2025,
}

\ctuprocess

\addto\ctucaptionsczech{%
	\def\supervisorname{Vedoucí}%
	\def\subfieldofstudyname{Studijní program}%
}

\ctutemplateset{maketitle twocolumn default}{
	\begin{twocolumnfrontmatterpage}
		\ctutemplate{twocolumn.thanks}
		\ctutemplate{twocolumn.declaration}
		\ctutemplate{twocolumn.abstract.in.titlelanguage}
		\ctutemplate{twocolumn.abstract.in.secondlanguage}
		\ctutemplate{twocolumn.tableofcontents}
		\ctutemplate{twocolumn.listoffigures}
	\end{twocolumnfrontmatterpage}
}


% Theorem declarations, this is the reasonable default, anybody can do what they wish.
% If you prefer theorems in italics rather than slanted, use \theoremstyle{plainit}
\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[chapter]
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{conjecture}[theorem]{Conjecture}

\theoremstyle{note}
\newtheorem*{remark*}{Remark}
\newtheorem{remark}[theorem]{Remark}

\setlength{\parskip}{3ex plus 0.2ex minus 0.2ex}


% Abstract in Czech
\begin{abstract-czech}
	Dnes je na trhu široká nabídka senzorů pro prostorové skenování; většina z nich je však příliš drahá pro amatérské využití.
	Cílem tohoto miniprojektu je navrhnout cenově dostupnou platformu pro 360$\degree$ \gls{lidar} senzor, která bude v navazující bakalářské práci využita k vytvoření 3D modelu naskenovaného prostředí.
	Práce analyzuje již existující DIY řešení, identifikuje jejich omezení a navrhuje konstrukci platformy, která tyto nedostatky omezuje.
	Výsledkem je modularní platforma, kterou lze rychle upravit podle požadavků uživatele.
\end{abstract-czech}



% Abstract in English
\begin{abstract-english}
	A wide range of \gls{lidar} sensors for spatial scanning is available on the market today; however, most remain too expensive for amateur use. 
	The aim of this miniproject is to design a cost-effective platform for a 360$\degree$ \gls{lidar} sensor, which will be utilised in a subsequent bachelor's thesis to obtain a 3D model of the scanned environment. 
	This work provides an overview of existing DIY solutions, evaluates their limitations and proposes a platform design that addresses the identified weaknesses. 
	The result is a configurable platform that can be quickly reassembled depending on whether the user prioritises more complete coverage or quicker scan.
\end{abstract-english}


% Acknowledgements / Podekovani
\begin{thanks}
	I am deeply grateful to my supervisor, Ing. Pavel Puričer, Ph.D., for his time and guidance during the work on this project. 
	I would also like to thank Ing. Jan Šístek, Ph.D., and Ing. František Rund, Ph.D., for their feedback on the homework assignments from the course "Technical Writing", 
	which was taken into account during the writing of this document.
\end{thanks}



% Declaration / Prohlaseni
\begin{declaration}
	I hereby declare that artificial intelligence was used during the writing of this thesis, specifically as an aid in generating TikZ figures. 
	Grammar was controlled with Grammarly.
	All generated content was verified, and I take full responsibility for the contents of this project. 
	All information taken from the work of other authors has been properly cited.
	
	In Prague, \ctufield{day}.~\monthinlanguage{title}~\ctufield{year}
\end{declaration}



% % Only for testing purposes
% \listfiles
% \usepackage[pagewise]{lineno}
% \usepackage{lipsum,blindtext}
% \usepackage{mathrsfs} % provides \mathscr used in the ridiculous examples


% CONTINUE HERE WITH THE DOCUMENT CONTENT
\begin{document}

\maketitle

\printglossary[type=\acronymtype]
\printunsrtglossary[title=Acronyms]

\chapter{Introduction}
\input{introduction/introduction.tex}

\chapter{Design of a Platform}
\input{design/design.tex}



\chapter{Conclusion}
\input{conclusion/conclusion.tex}

\appendix

\printindex

% \appendix


\printbibliography[title={Bibliography}]
\thispagestyle{plain}

% \ctutemplate{specification.as.chapter}

\end{document}